%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Using Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{empheq}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{color}
\usepackage{psfrag}
\usepackage{pgfplots}
\usepackage{bm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Other Settings

%%%%%%%%%%%%%%%%%%%%%%%%%% Page Setting %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\geometry{a4paper}

%%%%%%%%%%%%%%%%%%%%%%%%%% Define some useful colors %%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{ocre}{RGB}{243,102,25}
\definecolor{mygray}{RGB}{243,243,244}
\definecolor{deepGreen}{RGB}{26,111,0}
\definecolor{shallowGreen}{RGB}{235,255,255}
\definecolor{deepBlue}{RGB}{61,124,222}
\definecolor{shallowBlue}{RGB}{235,249,255}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%% Define an orangebox command %%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\orangebox[1]{\fcolorbox{ocre}{mygray}{\hspace{1em}#1\hspace{1em}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% English Environments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheoremstyle{mytheoremstyle}{3pt}{3pt}{\normalfont}{0cm}{\rmfamily\bfseries}{}{1em}{{\color{black}\thmname{#1}~\thmnumber{#2}}\thmnote{\,--\,#3}}
\newtheoremstyle{myproblemstyle}{3pt}{3pt}{\normalfont}{0cm}{\rmfamily\bfseries}{}{1em}{{\color{black}\thmname{#1}~\thmnumber{#2}}\thmnote{\,--\,#3}}
\theoremstyle{mytheoremstyle}
\newmdtheoremenv[linewidth=1pt,backgroundcolor=shallowGreen,linecolor=deepGreen,leftmargin=0pt,innerleftmargin=20pt,innerrightmargin=20pt,]{theorem}{Theorem}[section]
\theoremstyle{mytheoremstyle}
\newmdtheoremenv[linewidth=1pt,backgroundcolor=shallowBlue,linecolor=deepBlue,leftmargin=0pt,innerleftmargin=20pt,innerrightmargin=20pt,]{definition}{Definition}[section]
\theoremstyle{myproblemstyle}
\newmdtheoremenv[linecolor=black,leftmargin=0pt,innerleftmargin=10pt,innerrightmargin=10pt,]{problem}{Problem}[section]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Plotting Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepgfplotslibrary{colorbrewer}
\pgfplotsset{width=8cm,compat=1.9}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title & Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Econ 164 Problem Set 3}
\author{Nathaniel Marthen}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    \maketitle
    
    \section*{Question 1}
    The Minimum Support Price is a guaranteed price at which the government commits to buying select crops such as rice and wheat. It's purpose is to insulate farmers from income volatility, by preventing shifts in prices from market movements to affect the regular income for farmers.
    Benefits include food security and stability in the income of farmers.
    Costs include the accumulation of food stocks beyond buffer needs, some fiscal deficit and that it deters diversification of agriculture.
    Reforms could include the introduction of surveys or censuses to prevent the overstocking of food.\\


    The APMC provides monopsony rights to government-autorhized purchasing agents to procure agricultural produce at 'mandis'.
    It's purpose if to protect farmers from traders who exploit them through lower prices at the farmers' expense. 
    Benefits are skewed towards politicans who are controlling mandis. Also, agents still proliferate and buy from farmers at a lower price and bundle to achieve economies of scale. 
    Costs include the competitive entry for buyers who may offer better terms to farmers and better integration with storage and national markets.
    Reforms include the some facility to ensure proper trade is done with buyers.\\ 


    The fertilizer subsidies are subsidies provided to fertilizer companies to reduce prices paid by farmers for fertilizaers. It's purpose if to encourage farmers to use fertilizer to improve soil quality and hence agricultural yield to increase productivity.
    Benefits include increased food security.
    Costs include fiscal deficit, the encouragement of inefficient producers, and the distortion of cropping patters. 
    Reforms could include a tiered system which allocated more fertilizers to higher productivity farmers whilst punishing the less productive ones.\\
    
    The Public Distribution System is a network that provides subsidized foodgrains to targeted beneficiaries through government-run "Fair Price Shops". 
    It's purpose if to provide food security to the poor and offload surplus that was generated from MSP. 
    Benefits include food security for the poort and insulation against price volatility. 
    However, there is a lot of leakage, around 20 to 70\%. There is also reduced beneficiary flexibility and dietary diversity.\\ 
    \section*{Question 2}
    \section*{Question 3}
    \section*{Question 4}
    \subsection*{Part A}
    \subsection*{Part B}
    \subsection*{Part C}
    \section*{Question 5}
    \section*{Question 6}
    \subsection*{a.}
    \subsection*{b.}
    \subsection*{c.}
    \subsection*{d.}
    \subsection*{e.}

\end{document}
